BFS search in miniKanren

### 2019-03-06 Paper/paper.tex
descript mk-2

@@

The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
The order of the answers reflects the order miniKanren discovers them:
the leftmost answer is the first one. This result is not suprising:
to generate the first answer, \texttt{'()}, miniKanren needs to apply
\texttt{repeato} only once and the later answers need more recursive
applications. In this example, the cost of each answer is the same as
one more than the number of \texttt{*}s. The cost of \texttt{'()} is 1,
the cost of \texttt{'(*)} is 2, etc.

@@

(eqv to Seres's BFS ?)

Make irrelevant parts in mK representation-independent w.r.t. search space, and combine mature part and immature part with cons.

>>>>

miniKanren is a relational programming language embedable in many languages[cite
miniKanren.org?].

The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
an efficient and complete search strategy -- interleaving depth-first search (iDFS).
iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
organize their conde lines carefully. We proposed two search strategies and their
implementations. The first strategy is breadth-first search. The second one is a
modified iDFS.

@@

The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
The order of the answers reflects the order miniKanren discovers them:
the leftmost answer is the first one. This result is not suprising:
to generate the first answer, \texttt{'()}, miniKanren needs to apply
\texttt{repeato} only once and the later answers need more recursive
applications. In this example, the cost of each answer is the same as
one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
the cost of \texttt{'(*)} is 2, and so on.

@@

In \texttt{mk-2} we set up an interface between streams and the rest of miniKanren,
so that the optimization in \texttt{mk-3} is easier to present. As a side-effect, we
also solve the problem of copying too many \texttt{cons} cells. We list all interface functions in Fig.~\ref{interface-functions}.

\begin{figure}

\begin{tabular}{|c|c|}
\hline 
interface function & meaning \\ 
\hline 
empty-inf & construct an empty stream \\ 
\hline 
unit-mature-inf & construct a stream with one answer \\ 
\hline 
unit-immature-stream & construct a stream with one thunk \\ 
\hline 
null-inf? & predicate whether a stream is empty \\ 
\hline 
mature-inf? & predicate whether a stream has some mature answers \\ 
\hline 
car-inf & take the first answer out of a mature stream \\ 
\hline 
cdr-inf & remove the first answer of a mature stream \\ 
\hline 
force-inf & get answers of higher cost \\ 
\hline
\end{tabular}
	 \caption{interface functions and their meanings in mk-2 and mk-3}
	 \label{interface-functions}
\end{figure}

The representation of stream in \texttt{mk-2} is a pair of mature part and immature part. The mature parts are lists of answers. And the immature part is either a thunk or \texttt{'()}.

Changes in \texttt{mk-2} are mostly about setting up the interface, except the change in \texttt{append-inf} (Fig.~\ref{append-inf-2}). This version of \texttt{mk-2} essentially does the same thing as the \texttt{mk-1} version.

\begin{figure}
	 \lstinputlisting{Figures/append-inf-2.rkt}	
	 \caption{\texttt{append-inf} in \texttt{mk-2}}
	 \label{append-inf-2}
\end{figure}
